Building a GNU/Hurd Cluster

### 2019-06-03 doc/cua.tex
reorganize all docs into a 'doc' directory

\begin{frame}
\frametitle{Hurd Filesystem}
\tikzstyle{dirent}=[draw=black,thick,anchor=west]
\tikzstyle{selected}=[draw=red,fill=red!30]
\tikzstyle{optional}=[dashed,fill=gray!50]
\tikzstyle{link}=[red,dotted,->,thick]
\tikzstyle{grow2}=[grow via three points={one child at (1.5,0) and two children at (1.5,0) and (1.5,-0.7)},
  edge from parent path={(\tikzparentnode.east) -- +(.5,0) |- (\tikzchildnode.west)}]
\begin{center}
\begin{tikzpicture}
  [grow via three points={one child at (0.5,-0.7) and
  two children at (0.5,-0.7) and (0.5,-1.4)},
  edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}]
  \node[dirent] (root) {/}
  child { node[dirent] {bin}
    child [grow2] { node[dirent] (bash) {bash}}
    child [grow2] { node[dirent] (date) {date}}
    child [grow2] { node[dirent] (grep) {grep}}
    child [grow2] { node[dirent] (ls) {ls}}
  }
  child { node[dirent] {etc}}
  child { node[dirent] {lib}}
  child { node[dirent] {tmp}}
  child { node[dirent] (hurd) {hurd}}
  child { node[dirent] (home) {home}}
  child { node[dirent] (http) {http:}}
  child { node[dirent] {servers}
    child { node[dirent] {socket}
      child { node[dirent] (inet) {inet}}
    }
  };

\task{ext2 File Server}{at (20 em,-5 em)}{l}{}
\task{httpfs}{at (20 em, -12 em)}{ls}{}
\task{pfinet}{at (20 em, -17 em)}{ls}{}

@@

\draw [link] (http) -- +(2,0) |- (httpfs Port 0);
\draw [link] (inet) -- (pfinet Port -1);

>>>>

\begin{frame}
\frametitle{Hurd Filesystem}
\tikzstyle{dirent}=[draw=black,thick,anchor=west]
\tikzstyle{selected}=[draw=red,fill=red!30]
\tikzstyle{optional}=[dashed,fill=gray!50]
\tikzstyle{link}=[red,dotted,->,thick]
\tikzstyle{grow2}=[grow via three points={one child at (1.5,0) and two children at (1.5,0) and (1.5,-0.7)},
  edge from parent path={(\tikzparentnode.east) -- +(.5,0) |- (\tikzchildnode.west)}]
\begin{center}
\begin{tikzpicture}
  [node distance = 1em, grow via three points={one child at (0.5,-0.7) and
  two children at (0.5,-0.7) and (0.5,-1.4)},
  edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}]
  \node[dirent] (root) {/}
  child { node[dirent] {bin}
    child [grow2] { node[dirent] (bash) {bash}}
    child [grow2] { node[dirent] (date) {date}}
    child [grow2] { node[dirent] (grep) {grep}}
    child [grow2] { node[dirent] (ls) {ls}}
  }
  child { node[dirent] {etc}}
  child { node[dirent] {lib}}
  child { node[dirent] {tmp}}
  child { node[dirent] (hurd) {hurd}}
  child { node[dirent] (home) {home}}
  child { node[dirent] (http) {http:}}
  child { node[dirent] {servers}
    child { node[dirent] {socket}
      child { node[dirent] (inet) {inet}}
    }
  };

\task{ext2 File Server}{at (20 em,-5 em)}{l}{}
\task [below = of ext2 File Server] {httpfs}{}{ls}{}
\task [below = of httpfs] {pfinet}{}{ls}{}

@@

\draw [link] (http) -- (httpfs Port 1);
\draw [link] (inet) -- (pfinet Port -1);
